\documentclass[letterpaper,11pt,titlepage]{article}

\usepackage{graphicx}                                        

\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}                                          

\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}

\usepackage{url}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}

\usepackage{pstricks, pst-node}

\usepackage{geometry}
\geometry{textheight=10in, textwidth=7.5in}

\usepackage{listings}
\usepackage{multirow, booktabs, array}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ %
  basicstyle=\ttfamily,            % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=10pt,                  % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=8,                       % sets default tabsize to 8 spaces
  %title=\lstname                  % show the filename of files included with \lstinputlisting; also try caption instead of title
}

\lstdefinestyle{niceC}{
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  frame=L,
  xleftmargin=0.2in,
  language=C,
  showstringspaces=false,
  basicstyle=\footnotesize\ttfamily,
  keywordstyle=\bfseries\color{green!40!black},
  commentstyle=\itshape\color{purple!40!black},
  identifierstyle=\color{blue},
  stringstyle=\color{orange},
}

%random comment

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\usepackage{hyperref}

\def\name{Jianzhi Li}

%% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {cs444 ``operating systems II'' Project 4},
  pdftitle = {CS 444 Project 4: Write-up},
  pdfsubject = {CS 444 Project 4},
  pdfpagemode = UseNone
}

\parindent = 0.0 in
\parskip = 0.2 in

\usepackage{sectsty}


\sectionfont{\fontsize{12}{15}\selectfont}


\begin{document}


Jianzhi Li\newline
CS444 Project 4 Write-up

\section{Design Plan For SLOB Best-Fit Algorithm}

Before to design the best-fit algorithem. I was reviewed the knowledge of memory management and study each function of the original slob.c in the kernel. Also I did 
some research by read a few documents created by others that compared the difference between the first-fit algorithm and the best-fit algorithem. As the result, I should have a 
function that is can compare the size of memory block and find out a memory block that has the best-fit size. 
    




\section{Work Log}
\begin{enumerate}

\item Tuesday, 11/17/15. Start research on this project. I looked at a few documents on the internet, those documents are compared the first-fit algorithem and the best fit algorithm. Also reviewed the chapter 12 for memory management.

\item Wednesday, 11/18/15. Created the project folder on the github. I have going through the original code of slob.c which is used first-fit algorithm to allocate pages. 
\item Thursday, 11/05/15. Copied 'sbd.c' as my block device driver. Start going through each function.

\item Friday, 11/06/15. Located the function 'sbd transfer', that is the function I need add crypto API since there is the encrypts and decrypts function will operate the data. 
\item Sunday, 11/08/15. Some syntax problem with crypto API. There is too many of them in the introduction of crypto API. Most of them are struct. For doing that, I may just need take out encrypts and decrypts function from struct and put them in 'sbd transfer' function.

\item Monday, 11/09/15. Finished the crypto API, I have print function under each step of encryption and decryption which mean before and after. I tried to rebuild the kernel and fixed some bugs then that is working well. But I have a concern that is I do not know why the Makefile cannot give me the kernel object file. That is a problem to change to mount the ram disk driver. 
I tried to use 'insmod' to install the module but there was an error that is my object file have no permission to do that. 

\end{enumerate}


\section{Questions}
\begin{enumerate}

\item I think the main point for this assignment to let me learn how to use module in the linux kernel. Since if I want to be a kernel programmer, I have to learn module programming since that is an important part of the kernel. That is also a way how kernel programmer to improve kernel and add more functions and features in the kernel.
Also module as my understanding that is support hot plug which mean I can modify a module when the VM is running. I think that is also how the USB working in the operating system.

\item Be honest, the 'sbd.c' gives most of what I need in this assignment, all I need is to do is to figure out how to use crypto API. I can rebuild my kernel that is mean I do not have bugs in my code but that is not mean I do not have problem with the function of the code.

\item As I metioned in my work log. I do want to test my code that add that to be a module. But once I want to install my module that I would receive 'operation not permitted'. I would fix that as fast I can.

\item In this assignment, I learn how to use crypto API and concept of module and block devices as what Chapter 17 in our textbook that addressed. For install a module to a running VM and change the file system those are also important technique to learn. As I am not successful to test my correctness before the due date. I would figure that out before the demo. 

\end{enumerate} 


\section{Verison Control Log}

\begin{table}[!hbp]
\begin{tabular}{|c|}

\hline
Author: lijian $<lijian@os-class.engr.oregonstate.edu>$\\
Date:   Mon Nov 9 23:58:14 2015 -0800\\

    upload proj3\\

\hline
commit fb925285c888639726684e74511f71eab345313f\\
Author: lijian $<lijian@os-class.engr.oregonstate.edu>$\\
Date:   Mon Nov 9 13:26:03 2015 -0800\\

    untest version of ramdisk\\

\hline
commit 963de9778620f69ce85f4ca95a3772f6efaad489\\
Author: lijian $<lijian@os-class.engr.oregonstate.edu>$\\
Date:   Mon Nov 2 18:09:20 2015 -0800\\

    project3 created\\

\hline


 
\end{tabular}
\end{table}








\end{document}